### 2022-05-12 paper/localpsf.tex
fix typos, minor wordsmithing, in low rank update appendix

\section{Ellipsoid intersection test}
\label{sec:fast_ellipsoid_intersection_test}
The procedure for choosing sample points relies on quickly determining whether two ellipsoids intersect. Let $E_1$ and $E_2$ be the ellipsoids defined as
\begin{align*}
	E_1 :=& \{x : (x - \spatialmean_1)^T \spatialcov_1^{-1} (x - \spatialmean_1) \le \tau^2\} \\
	E_2 :=& \{x : (x - \spatialmean_2)^T \spatialcov_2^{-1} (x - \spatialmean_2) \le \tau^2\}, \\
\end{align*}
where $\spatialmean_1, \spatialmean_2 \in \mathbb{R}^\gdim$, and $\spatialcov_1, \spatialcov_2 \in \mathbb{R}^{\gdim \times \gdim}$ are positive definite. Let $K$ be the following one dimensional convex function:
\begin{equation*}
	K(s) := 1 - \frac{1}{\tau^2} (\spatialmean_1 - \spatialmean_2)^T \left(\frac{1}{1-s}\spatialcov_1 + \frac{1}{s}\spatialcov_2\right)^{-1}(\spatialmean_1 - \spatialmean_2)	
\end{equation*}
In \cite{GilitschenskiHanebeck12} it is shown that $E_1 \cap E_2 = \{\}$ if and only if $K(s) < 0$ for some $s\in (0,1)$. We check whether $E_1$ and $E_2$ intersect by minimizing $K(s)$ on $(0,1)$. If $K(s^*) <0$ at the minimizer $s^*$, then $E_1 \cap E_2 = \{\}$. Otherwise $E_1 \cap E_2 \neq \{\}$.

@@

In all three cases, direct calculation shows that we have $\mathbf{P}^{(k+1)}\mathbf{Y}=\mathbf{X}$, which implies $\left(\mathbf{P}^{(k+1)}\right)^{-1} \mathbf{X} = \mathbf{B}^{(k)}\mathbf{X}$. Formulas \eqref{eq:res_update} and \eqref{eq:srk_update} perform rank-$m$ updates, while formula \eqref{eq:dfp_update} performs a rank-$2m$ update. Formula \eqref{eq:res_update} does not preserve symmetry, and should therefore be used when $\mathbf{B}^{(k)}$ is not symmetric. Formula \eqref{eq:srk_update} preserves symmetry but not positive definiteness, and should therefore be used when $\mathbf{B}^{(k)}$ is symmetric and indefinite. Formula \eqref{eq:dfp_update} preserves both symmetry and positive definiteness, and should therefore be used when $\mathbf{B}^{(k)}$ is symmetric positive definite. Formula \eqref{eq:srk_update} is known as the ``symmetric rank-$m$'' update formula. Formula \eqref{eq:dfp_update} is known as the DFP update formula, named after it's inventor Davidson, and polularizers Fletcher and Powell. For more details on these update formulas, we recommend the discussion in Chapter 6 of \cite{NocedalWright99}. In \cite{NocedalWright99}, one-vector versions of formulas \eqref{eq:srk_update} and \eqref{eq:dfp_update} are discussed thoroughly; the versions here are straightforward generalizations to many-vector updates.

>>>>

\section{Ellipsoid intersection test}
\label{sec:fast_ellipsoid_intersection_test}
The procedure for choosing sample points relies on quickly determining whether two ellipsoids intersect. Let $E_1$ and $E_2$ be the ellipsoids defined as
\begin{align*}
	E_1 :=& \{x : (x - \spatialmean_1)^T \spatialcov_1^{-1} (x - \spatialmean_1) \le \tau^2\}, \\
	E_2 :=& \{x : (x - \spatialmean_2)^T \spatialcov_2^{-1} (x - \spatialmean_2) \le \tau^2\}, \\
\end{align*}
where $\spatialmean_1, \spatialmean_2 \in \mathbb{R}^\gdim$, and $\spatialcov_1, \spatialcov_2 \in \mathbb{R}^{\gdim \times \gdim}$ are positive definite. Let $K$ be the following one dimensional convex function:
\begin{equation*}
	K(s) := 1 - \frac{1}{\tau^2} (\spatialmean_1 - \spatialmean_2)^T \left(\frac{1}{1-s}\spatialcov_1 + \frac{1}{s}\spatialcov_2\right)^{-1}(\spatialmean_1 - \spatialmean_2)	
\end{equation*}
In \cite{GilitschenskiHanebeck12} it is shown that $E_1 \cap E_2 = \{\}$ if and only if $K(s) < 0$ for some $s\in (0,1)$. We check whether $E_1$ and $E_2$ intersect by minimizing $K(s)$ on $(0,1)$. If $K(s^*) <0$ at the minimizer $s^*$, then $E_1 \cap E_2 = \{\}$. Otherwise $E_1 \cap E_2 \neq \{\}$.

@@

In all three cases, direct calculation shows that we have $\mathbf{P}^{(k+1)}\mathbf{Y}=\mathbf{X} = \left(\mathbf{B}^{(k)}\right)^{-1} \mathbf{Y}$. Formulas \eqref{eq:res_update} and \eqref{eq:srk_update} perform rank-$m$ updates, while formula \eqref{eq:dfp_update} performs a rank-$2m$ update. Formula \eqref{eq:res_update} does not preserve symmetry, and should therefore be used when $\mathbf{B}^{(k)}$ is not symmetric. Formula \eqref{eq:srk_update} preserves symmetry but not positive definiteness, and should therefore be used when $\mathbf{B}^{(k)}$ is symmetric and indefinite. Formula \eqref{eq:dfp_update} preserves both symmetry and positive definiteness, and should therefore be used when $\mathbf{B}^{(k)}$ is symmetric positive definite. When $m=1$, formula \eqref{eq:srk_update} is known as the SR1 (``symmetric rank-$1$'') update formula, and formula \eqref{eq:dfp_update} is known as the DFP update formula, which is named after it's inventor Davidson, and popularizers Fletcher and Powell. For more details on these update formulas, we recommend the discussion in Chapter 6 of \cite{NocedalWright99}. In \cite{NocedalWright99}, one-vector versions of formulas \eqref{eq:srk_update} and \eqref{eq:dfp_update} are discussed thoroughly; the versions here are straightforward generalizations to many-vector updates.
